Scalar on Function Regression \\ with Applications to Near-Infrared Spectroscopy

### 2022-01-15 Presentation/slides.tex
Slide Update

	% Title page frame
	\begin{frame}
		\titlepage 
	\end{frame}

@@

	%\begin{frame}{Theory}
	%	Jonghun
	%	\begin{itemize}
	%		\item Random Functions (name square integrable functions)
	%		\item Motivate continuous stochastic processes (growth curves/electricity consumption/yield curves/stonks)
	%		\item Use curves to predict a scalar response (show typical dgp)
	%	\end{itemize}
	%\end{frame}

	%\begin{frame}{Theory}
	%	Jonghun
	%	\begin{itemize}
	%		\item Basis expansions (b-splines and fourier)
	%		\item Talk about purposes
	%		\item Plots and show bias variance tradeoff
	%	\end{itemize}
	%\end{frame}

	\begin{frame}{Random Function}
		A \textbf{Random Variable} is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ then $X$ is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ then $X$ is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a \textbf{Random Function}
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Two Typical Types of Basis Function}
		\textbf{Fourier Basis Function} is an element of the set:

		$$\{\sqrt{2}sin(2\pi nx | n \in \mathbb{N})\} \cup \{\sqrt{2}cos(2\pi nx | n \in \mathbb{N})\} \cup \{1\}$$

		%$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\

		\vspace{2\baselineskip}
		\textbf{B-spline Basis Function} is a polynomial function defined by order and knots. \\

@@

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Fourier_Basis.pdf}
			\caption {Fourier basis functions}
		\end{figure}

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
			\caption {Bspline basis functions}
		\end{figure}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		We can transform the data generating process into:
		\begin{equation}\notag
			\begin{split}
				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} c_j  \phi_j(s)\right) X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
						  & = \alpha + \sum_{j = 1}^{\infty} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
						  & = \alpha + \sum_{j = 1}^{\infty} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  
			\end{split}
		\end{equation}

@@

	\begin{frame}{Estimation via Basis Representation}
		Each combination of $x_i(t)$ and $\phi_j(t)$ gives us
		$$Z_{i,j} = \int_{0}^{1} x_i(s) \phi_j(s)\mathrm{d}s$$

		\begin{itemize}
			\item This allows us to write each observation in the data set as $\left(y_i, Z_{i,1}, Z_{i,2}, \dots \right)$
			\item Truncating the functional basis yields an approximation $\left(y_i, Z_{i,1}, Z_{i,2}, \dots, Z_{i,L}\right)$
		\end{itemize}

		Coefficients can then be estimated using theory from \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$.
	\end{frame}

	\begin{frame}{Estimation via Basis Representation}
		This can be translated into an estimated coefficient function $\hat{\beta}(t)$:

		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{c}_{L,j} \phi_j(t)$$

		This is dependent on...
		\begin{itemize}
			\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
			\item The truncation parameter $L$
			\item The basis $(\psi_j(t))_{j \in \mathcal{I}}$ used for the expansion of the observations
			\item The truncation parameter in the approximation of the observations $K$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{FPCA - Plot}
			%\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
	\end{frame}

@@

	\begin{frame}{Simulation Results - bspline}
		\begin{table}
		\centering
\resizebox*{\columnwidth}{!}{%
\begin{tabular}{lllllll}
\cline{2-6}
 & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
 & 2.02918344408687                       & {\color[HTML]{FD6864} 72.0085477229407} & 0.511999648510189                         & 1.47468049635309                         & 3                &  \\
 & {\color[HTML]{FD6864} 2.0220366421201} & 72.60172284215                          & 0.16157756089415                          & 1.13746697354709                         & 5                &  \\
 & 2.0354924731897                        & 73.1836346250812                        & 0.0293072016650537                        & {\color[HTML]{FD6864} 0.990682620987463} & 7                &  \\
 & 2.06199840536677                       & 73.9631412481736                        & {\color[HTML]{FD6864} 0.0290190767234641} & 0.999385186246351                        & 9                &  \\
 & 2.08808310984254                       & 75.0920660376146                        & 0.0290873388349217                        & 1.01393568534507                         & 11               &  \\
 & 2.09974789215127                       & 75.9422236701681                        & 0.0294100223429063                        & 1.02909474969485                         & 13               &  \\
 & 2.1086767501285                        & 76.7123085769457                        & 0.0298036585996321                        & 1.03713735705978                         & 15               &  \\
 & 2.13013296583489                       & 77.4907530428231                        & 0.0300236821233963                        & 1.03980406503428                         & 17               &  \\
 & 2.15348157839283                       & 78.3942553410957                        & 0.030307463717998                         & 1.0508902800978                          & 19               &  \\
 & 2.17750745519215                       & 79.2057575714294                        & 0.0306501467540424                        & 1.06172373892826                         & 21               &  \\
 & 2.20581113466118                       & 80.3800790338639                        & 0.0309985992677207                        & 1.07695651700849                         & 23               &  \\
 & 2.23717951397715                       & 81.5089652049561                        & 0.0314869147262958                        & 1.09052842774153                         & 25               & 
\end{tabular}%
}
\end{table}
	\end{frame}

@@

	\begin{frame}{Summary}
		\begin{itemize}
		\item
    		Concepts of functional data: 
    		\begin{itemize}
			\item See dataset as smooth curve than as set of discrete measurements.
    			\item Theory of Random Functions, motivated from random variable.
    			\item Basis expansion and its Bias-Variance tradeoff.
    			\item Scalar on Function Regression via Basis Expansion.
    			\item Functional principal component Analysis and FPCR.
		\end{itemize}
    		\item
    		Simulation study results: specification depends on function and signal-to-noise ratio
    		\item
    		% Guided you  from the beginning to the end of the presentaion through one application ....
    		Guided through application to predict octane ratings.

	\begin{frame}
		\topskip0pt
		\vspace*{\fill}
		\begin{center}
			{\LARGE Thank you for your time!}
		\end{center}	
		\vspace*{\fill}
		%
	\end{frame}

	\begin{frame}{Further Reading}
		 Further Reading:
		 \nocite{Bohacs_Ovadi_Salgo1998}
		 \nocite{FR_li_et_al_2020} 
		 \nocite{Reiss_2007b}
		 \AtNextBibliography{\tiny}
		 \printbibliography[heading=none]
	\end{frame}

>>>>

	% Title page frame
	\begin{frame}
		\titlepage 
		\begin{center}
			{\small
			Research Module in Econometrics and Statistics \\
			Winter Semester 2021/2022}
		\end{center}
	\end{frame}

@@

	\begin{frame}{Random Function}
		A \textbf{Random Variable} is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\vspace{0.2cm}

		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ then $X$ is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ then $X$ is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a \textbf{Random Function}
		\end{itemize}
	\end{frame}

@@

	%\begin{frame}{Two Typical Types of Basis Function}
	%	\textbf{Fourier Basis Function} is an element of the set:
	%	
	%	$$\{\sqrt{2}sin(2\pi nx | n \in \mathbb{N})\} \cup \{\sqrt{2}cos(2\pi nx | n \in \mathbb{N})\} \cup \{1\}$$
	%	
	%	%$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
	%	
	%	\vspace{2\baselineskip}
	%	\textbf{B-spline Basis Function} is a polynomial function defined by order and knots. \\

	%\end{frame}

	\begin{frame}{Basis Functions}
		\textbf{Fourier Basis Functions} are elements of the set:
		$$\{\sqrt{2}\sin(2\pi nx) | n \in \mathbb{N}\} \cup \{\sqrt{2}\cos(2\pi nx) | n \in \mathbb{N}\} \cup \{1\}$$
		\vspace{-0.5cm}
		\begin{figure}
			\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
			%\caption {Fourier basis functions}
		\end{figure}

@@

	\begin{frame}{Basis Functions}
		\textbf{B-spline Basis Functions} are polynomial functions defined by an order and a set of knots.
		\begin{figure}
			\includegraphics[width = \textwidth]{../Graphics/Bspline_Basis.pdf}
			%\caption {Bspline basis functions}
		\end{figure}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		We can transform the data generating process into:
		\begin{equation}\notag
			\begin{split}
				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} c_j  \phi_j(s)\right) X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
						  & = \alpha + \sum_{j = 1}^{\infty} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
						  & = \alpha + \sum_{j = 1}^{\infty} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  \approx  \alpha + \sum_{j = 1}^{L} c_j {\color{red}Z_j(\omega)}  + \epsilon(\omega)
			\end{split}
		\end{equation}

@@

	\begin{frame}{Estimation via Basis Representation}
		Truncating the functional basis allows us to estimate coefficients using \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$ and an approximated coefficient function $\hat{\beta}(t)$:
		\vspace{-0.2cm}
		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{c}_{L,j} \phi_j(t)$$

		This is dependent on...\vspace{-0.2cm}
		\begin{multicols}{2}
			\begin{itemize}
				\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
				\item The truncation parameter $L$\vfill\null
				\item The basis $(\psi_j(t))_{j \in \mathcal{I}}$ used for the observations
				\item The truncation parameter for the observations $K$
			\end{itemize}
		\end{multicols}

@@

	\begin{frame}{FPCA - Plot}
			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
	\end{frame}

@@

	\begin{frame}{Simulation Results - Fourier}
		\begin{table}
		\centering
\resizebox*{\columnwidth}{!}{%
\begin{tabular}{lllllll}
\cline{2-6}
 & \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
 & 2.02918344408687                       & {\color[HTML]{FD6864} 72.0085477229407} & 0.511999648510189                         & 1.47468049635309                         & 3                &  \\
 & {\color[HTML]{FD6864} 2.0220366421201} & 72.60172284215                          & 0.16157756089415                          & 1.13746697354709                         & 5                &  \\
 & 2.0354924731897                        & 73.1836346250812                        & 0.0293072016650537                        & {\color[HTML]{FD6864} 0.990682620987463} & 7                &  \\
 & 2.06199840536677                       & 73.9631412481736                        & {\color[HTML]{FD6864} 0.0290190767234641} & 0.999385186246351                        & 9                &  \\
 & 2.08808310984254                       & 75.0920660376146                        & 0.0290873388349217                        & 1.01393568534507                         & 11               &  \\
 & 2.09974789215127                       & 75.9422236701681                        & 0.0294100223429063                        & 1.02909474969485                         & 13               &  \\
 & 2.1086767501285                        & 76.7123085769457                        & 0.0298036585996321                        & 1.03713735705978                         & 15               &  \\
 & 2.13013296583489                       & 77.4907530428231                        & 0.0300236821233963                        & 1.03980406503428                         & 17               &  \\
 & 2.15348157839283                       & 78.3942553410957                        & 0.030307463717998                         & 1.0508902800978                          & 19               &  \\
 & 2.17750745519215                       & 79.2057575714294                        & 0.0306501467540424                        & 1.06172373892826                         & 21               &  \\
 & 2.20581113466118                       & 80.3800790338639                        & 0.0309985992677207                        & 1.07695651700849                         & 23               &  \\
 & 2.23717951397715                       & 81.5089652049561                        & 0.0314869147262958                        & 1.09052842774153                         & 25               & 
\end{tabular}%
}
\end{table}
	\end{frame}

@@

	%\begin{frame}{Summary}
	%	\begin{itemize}
	%	\item
    %		Concepts of functional data: 
    %		\begin{itemize}
	%		\item See dataset as smooth curve than as set of discrete measurements.
    %			\item Theory of Random Functions, motivated from random variable.
    %			\item Basis expansion and its Bias-Variance tradeoff.
    %			\item Scalar on Function Regression via Basis Expansion.
    %			\item Functional principal component Analysis and FPCR.
	%	\end{itemize}
    %		\item
    %		Simulation study results: specification depends on function and signal-to-noise ratio
    %		\item
    		% Guided you  from the beginning to the end of the presentaion through one application ....
    %		Guided through application to predict octane ratings.

	%	\end{itemize}
	%\end{frame}

	\begin{frame}{Further Reading}
		\nocite{hsing_theoretical_2015}
		\nocite{kokoszka_introduction_2017}
		\nocite{Bohacs_Ovadi_Salgo1998}
		\nocite{FR_li_et_al_2020} 
		\nocite{Reiss_2007b}
		\nocite{ramsay_functional_2005}
		\AtNextBibliography{\tiny}
		\printbibliography[heading=none]
	\end{frame}
